Loop-Aware Optimizations in PyPy's Tracing JIT

### 2012-08-07 talk/dls2012/paper.tex
typos

Loop invariant code motion optimizations are completely
standard~\cite{muchnick_advanced_1997}. Therefore, the effects that our
optimization achieves is not in any way new. However, we think that achieving
it as described in this paper is simpler than explicit algorithms.

>>>>

Loop invariant code motion optimizations are completely
standard~\cite{muchnick_advanced_1997}. Therefore, the effects that our
optimization achieves are not in any way new. However, we think that achieving
them in the way described in this paper is simpler than writing explicit algorithms.
